\documentclass[a4paper,10pt]{article}
%opening
\title{X Server Test Cases}
\author{Semen Cirit}

\begin{document}

\maketitle

 Note:	
  	For all X errors you can look the below file
	/var/log/Xorg.0.log  
\begin{enumerate}
  \item Testing direct rendering
    \begin{enumerate}
    \item  Hit $Ctrl+Alt+F1$

	    Observe that X doesn't crash.
    \item  Then execute this command:
	  \begin{verbatim}
	  xinit -- :2
	  \end{verbatim}
	  Observe a Grey desktop, and X for the mouse cursor and a term window.
    \item Hit \texttt{Ctrl+Alt+F7} to get back to the graphical environment:
    
	  Observe that X doesn't crash.
    \item Type commands "glxgears" and then "glxgears -fullscreen".

	  Observe that they run without any problem.
    \end{enumerate}

  \item DPI testing
    
        Run openoffice writer and open an A4 paper with 100\% zoom. Take also a real A4 paper.

        Observe that the width and the height of the real A4 are same with the open office writer's one.
  \item Resolution testing
     \begin{enumerate}
      \item Open systemsettings $\rightarrow$ Display

	Observe that the default resolution of the computer is selected for the current resolution.
      \item You can also observe it from the output of the "xrandr" command
	  
	  The example output of the command is like:
	  
	  1440x900  50.0*+
	  
	  This information means:
	  \begin{table}[h]
	  \centering
	  \begin{tabular}{|c|c|c|}
		  \hline
		  $1440x900$ & $\rightarrow$ & resolution \\
		  50.0       & $\rightarrow$ & refresh rate \\
		  $*$        & $\rightarrow$ & selected resolution is current resolution \\
		  $+$        & $\rightarrow$ & selected resolution is default resolution \\
		  \hline
	  \end{tabular} 
	  \label{tab:tbl}
	  \end{table}
    \end{enumerate}
 \item  Run a media player and open in full screen mode.

      Observe that X doesn't crash.
 \item Open desktop effects from system settings $\rightarrow$ desktop
 
      Observe that X doesn't crash
  \item 2D testing 
      
      Run a window, (for example dolphin, firefox) then swing it to right and left rapidly.
        Observe that it can swing without any problem.

 \item 3D testing
   %(For Pardus 2008 first execute glxinfo and find the Direct rendering is yes.)

    Run from kmenu education $\rightarrow$ science $\rightarrow$ marble
	
    Observe that the application is working flawlessly in terms of graphical rendering.
    \end{enumerate}
\end{document}
