\documentclass[a4paper,10pt]{article}

\title{Network Manager}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle

\begin{enumerate}
\item Create profile button
    \begin{enumerate}
    \item For wireless connections
        \begin{enumerate}
        \item Try to scan for a wireless network
    
            After searching a wireless network observe that security type is correctly found.
        \item Try to add this wireless network password and enable hide password.
    
            Observe the situation.
        \end{enumerate}
    \end{enumerate}

    \begin{enumerate}
    \item For ethernet or wireless connections
        \begin{enumerate}
        \item If you have more than one network connection, try to select a device from combobox.
        \item Try to create a new profile without adding a new name
            \begin{enumerate}
            \item Without adding a new name
    
                Observe that it gives a warning about the profile name and prevents to create the new profile.
    
            \item Add a new name and use DHCP and  and try to add this profile
            \end{enumerate}

        \item Name server settings button.
            \begin{enumerate}
            \item testcases will be added later.
            \end{enumerate}
        \end{enumerate}
    \end{enumerate}

\item Profiles part
    \begin{enumerate}
    \item Try to remove a profile.
    \item Try to change the configurations of a profile.
        \begin{enumerate}
        \item Try to change the profile name
        \item Network settings
            \begin{enumerate}
            \item Use DHCP
                \begin{itemize}
                \item Use custom address and network mask.
                \item Use custum default gateway.
                \end{itemize}
            \item Use Manual settings
            \end{enumerate}

        \item Name servers
            \begin{enumerate}
            \item Use Default
            \item Use Automatic
            \item Use Custom
            \end{enumerate}
        \item Apply them and observe the output of the below command.
        \end{enumerate}

        Execute the following command:
\begin{verbatim}
    # ping 4.2.2.1
\end{verbatim} 
    \end{enumerate}
\end{enumerate}

\end{document}