\documentclass[a4paper,10pt]{article}
%opening
\title{X Test Cases}
\author{Semen Cirit}

\begin{document}

\maketitle

 Note:	
  	For all X errors you can look the below file
	/var/log/Xorg.0.log  
\begin{enumerate}
  \item Testing direct rendering
    \begin{enumerate}
    \item  Push $Ctrl+Alt+F1$

	    Observe that X doesn't crash.
    \item  Then execute this command:
	  \begin{verbatim}
	  xinit -- :2
	  \end{verbatim}
	  Observe a Grey desktop, and X for the mouse cursor and a term window.
    \item Get back with pushing $Ctrl+Alt+F7$
    
	  Observe that X doesn't crash.
    \item Type commands "glxgears" and then "gleaxgears -fullscrean".

	  Observe that they run without any problem.
    \end{enumerate}

  \item DPI testing
    
        Run open office writer and open a A4 paper with 100\% zoom. Take also a real A4 papper.

        Observe that the width and the height of the real A4 are same with the open office writer's.
  \item Resolution testing
     \begin{enumerate}
      \item Open system settings $\rightarrow$ Display

	Observe that the default resolution of the computer is selected for the current resolution.
      \item You can observe it from also, typing command "xrandr". 
	  
	  The example output of the command is like:
	  
	  1440x900  50.0*+
	  
	  This information means:
	  \begin{table}[h]
	  \centering
	  \begin{tabular}{|c|c|c|}
		  \hline
		  $1440x900$ & $\rightarrow$ & resolution \\
		  50.0       & $\rightarrow$ & refresh rate \\
		  $*$        & $\rightarrow$ & selected resolution is current resolution \\
		  $+$        & $\rightarrow$ & selected resolution is default resolution \\
		  \hline
	  \end{tabular} 
	  \label{tab:tbl}
	  \end{table}
    \end{enumerate}
 \item  Run a media player and open in full screen mode.

      Observe that X doesn't crash.
 \item Open desktop effects from system settings $\rightarrow$ desktop
 
      Observe that X doesn't crash
  \item 2D testing 
      
      Run a window, (for example dolphin, firefox) then swing it to right and left rapidly.
        Observe that it can swing without any problem.

 \item 3D testing
   %(For Pardus 2008 first execute glxinfo and find the Direct rendering is yes.)

    Running google earth
     \begin{enumerate}
      \item Download the bin file from http://earth.google.com/
      \item Open the directory which the bin file downloaded.
	\begin{verbatim}
	cd <bin_file_directory>
	\end{verbatim}
      \item Make it executable
	\begin{verbatim}
	chmod 755 GoogleEarthLinux.bin
	\end{verbatim}
      \item Install it 
	\begin{verbatim}
	./GoogleEarthLinux.bin
	\end{verbatim}
      \item Run it and observe that the application apparition is problem-free.
    \end{enumerate}
\end{enumerate}
\end{document}
