\documentclass[a4paper,10pt]{article}

\title{Spam Filter Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle

\begin{enumerate}
	\item After installing the related package.
	\item Open Kmail then add activate this spam filter.
		
	\begin{enumerate}
		\item Click tools $\rightarrow$  Anti-Spam Wizard.
		\item Select the related spam filter that you installed.
		\item Right click on to a mail then select from the combobox Apply Filter $\rightarrow$ Filter Classify as Spam 
		Observe that this mail goes to related spam folder.(The default spam folder is trash.)
		\item Download the gtube.txt from: 
		\begin{verbatim}
 		http://spamassassin.apache.org/gtube/
		\end{verbatim}
		\item  Execute this command:
		\begin{verbatim}
 		cat  gtube.txt | spamc 
		\end{verbatim}
		
		This command will give you an output like this:
		
		\emph{If your spam filter supports it, the GTUBE provides a test by which you
	    	can verify that the filter is installed correctly and is detecting incoming
    		spam. You can send yourself a test mail containing the following string of
    		characters (in upper case and with no white spaces and line breaks):}
		\begin{verbatim}
 		XJS*C4JDBQADN1.NSBN3*2IDNEN*GTUBE-STANDARD-ANTI-UBE-TEST-EMAIL*C.34X
		\end{verbatim}
    		\emph{You should send this test mail from an account outside of your network.}

		\item Then copy the above part and send it to yourself.
		
		Observe that this mail directly goes to related spam folder.
	\end{enumerate} 
 


\end{enumerate}

\end{document}




